Water discharge quantity has a variable impact on sediment transport capacity in subglacial channels

### 2023-09-21 Delaneyetal2023b.tex
small bits

Regardless of the increased performance of water discharge compared to subglacial sediment transport capacity in the observations, parameterization outputs suggest that additional processes and erosional hiatuses may further complicate signals of sediment discharge from glaciers in response to climate, compared to subaerial systems \cite{jansson2005,ganti2016}.
Sediment discharge records have been used to establish the relationship, or lack thereof, between climate forcing and glacial erosion \cite<e.g.>{koppes2009a,ganti2016,willenbring2016,mariotti2021}.
The variable relationship between water discharge and subglacial sediment transport capacity presented here mostly applies to the daily- to weekly-time scales controlling the size of subglacial channels (Figure~\ref{fig:multi_run}).
Yet, identifying climatic signals in sediment transport from the transport-limited component of glacier-sedimentary systems may require higher thresholds of water discharge compared to subaerial systems when water discharge varies substantial over short timescales \cite<Figure~\ref{fig:Qw_vari}; >{tofelde2021}.

@@

\section*{Author Contributions}
\ian{let me know if these accurately describe your contributions... I hope I am not leaving anything out}
I.D. designed the study, developed and implement the model and experiments and lead the writing.
D.F. provided data from Fieschergletscher.
A.J.T. helped interpret data from Leverett Glacier and provided guidance on experiment design.
M.A.W. provided data from Fieschergletscher, added the relationship between shear stress and water discharge (see Section~\ref{sect:dis_qsc} and Supplement).
All authors provided  key inputs in writing and editing the manuscript.

>>>>

Regardless of the increased performance of water discharge compared to subglacial sediment transport capacity in the observations, parameterization outputs suggest that additional processes and erosional hiatuses may further complicate signals of sediment discharge from glaciers in response to climate, compared to subaerial systems \cite{jansson2005,ganti2016}.
Sediment discharge records have been used to establish the relationship, or lack thereof, between climate forcing and glacial erosion \cite<e.g.>{koppes2009a,ganti2016,willenbring2016,mariotti2021}.
The variable relationship between water discharge and subglacial sediment transport capacity presented here mostly applies to the daily- to weekly-time scales controlling the size of subglacial channels (Figure~\ref{fig:multi_run}).
Yet, identifying climatic signals in sediment transport from the transport-limited component of glacier-sedimentary systems may require higher thresholds of water discharge compared to subaerial systems when water discharge varies substantially over short timescales \cite<Figure~\ref{fig:Qw_vari}; >{tofelde2021}.

@@

\section*{Author Contributions}
\ian{let me know if these accurately describe your contributions... I hope I am not leaving anything out}
I.D. designed the study, developed, designed, and implemented the model and experiments, and wrote the manuscript.
D.F. provided data from Fieschergletscher.
A.J.T. helped interpret data from Leverett Glacier and provided guidance on experiment design.
M.A.W. provided data from Fieschergletscher and added the relationship between shear stress and water discharge (see Section~\ref{sect:dis_qsc} and \ref{sect:scaling}).
All authors provided  key inputs in writing and editing the manuscript.
